\documentclass[letterpaper,10pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

% Section formatting
\titleformat{\section}{\large\bfseries\vspace{-4pt}}{}{0em}{}[\vspace{-6pt}\rule{\linewidth}{0.4pt}\vspace{-4pt}]

% Compact spacing
\setlength{\parskip}{3pt}
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=*}

\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\LARGE \textbf{Rijul Thakur}}\\[-2pt]
    +91-9816871545 \; | \; \href{mailto:rijulthakur34@gmail.com}{rijulthakur34@gmail.com} \; | \;
    \href{https://www.linkedin.com/in/rijul-thakur-7a1b89310/}{linkedin} \; | \;
    \href{https://github.com/rijulthakur34-glitch}{github.com/rijulthakur34-glitch} \; | \;
    \href{https://leetcode.com/u/falloff/}{leetcode}
\end{center}

% ---------- EDUCATION ----------
\section{Education}
\textbf{Bennett University}, Greater Noida \hfill \textit{2023 -- 2027}  
\textit{B.Tech in Computer Science \& Engineering} \hfill \textit{CGPA: 8.5/10 (Expected)}

% ---------- EXPERIENCE ----------
\section{Experience}
\textbf{Sheeva.AI}, Remote \hfill \textit{July 2024 -- Present}  
\textit{Artificial Intelligence Intern}
\begin{itemize}
    \item Developed and optimized RAG (Retrieval-Augmented Generation) pipelines for intelligent automotive search.
    \item Implemented high-performance inference using Groq LPU technology, reducing latency by 40\%.
    \item Collaborated on building vector database architectures for real-time data retrieval.
\end{itemize}

\textbf{Artificial Intelligence Internship (Task 1)}, Project \hfill \textit{May 2024}  
\textit{AI HR Shortlisting Agent Developer}
\begin{itemize}
    \item Built an end-to-end recruitment agent using Llama 3.3 and LangChain for automated resume scoring.
    \item Integrated "Agentic" reasoning to provide comparative candidate summaries and skill gap analysis.
    \item Developed a premium Glassmorphism dashboard in Streamlit with real-time dynamic weighting for scoring.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
\textbf{Recruitly} | \textit{Python, LangChain, Groq, Streamlit} \hfill \href{https://github.com/rijulthakur34-glitch/ai-hr-shortlisting-agent}{GitHub}
\begin{itemize}
    \item Developed a multi-agent system that evaluates resumes against JDs with 95\% structural accuracy.
    \item Features include automatic interview question generation and professional HTML report exporting.
    \item Deployed as a live web application on Streamlit Community Cloud.
\end{itemize}

\textbf{Campus Q\&A RAG Bot} | \textit{Python, LlamaIndex, OpenAI} \hfill \textit{Feb 2024}
\begin{itemize}
    \item Created a campus-wide assistant that answers student queries using internal university documentation.
    \item Reduced manual information desk queries by 30\% during initial pilot testing.
\end{itemize}

% ---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\textbf{Languages}: Python, C++, Java, JavaScript, SQL, LaTeX  
\textbf{AI/ML}: LangChain, LlamaIndex, RAG, Prompt Engineering, Vector Databases (Pinecone, Chroma)  
\textbf{Tools}: Git, Docker, Streamlit, FastAPI, Linux  

\end{document}
